EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-08 draft.tex
Updated Developer
addressing @jj comments

In the case of the first level of integration, a decoupled worker, % a decoupler worker what? - JJ
developers
can implement a new stateless Docker container following the description in the previous section (\ref{workers}). The worker
container executes a daemon that continuously pulls messages from the input queue
on the Redis host specified as an environment variable {\texttt REDIS\_HOST}. If the new
population-based algorithm is written in Python, developers can base the new
implementation on the provided worker container image, adding a new algorithm
function and worker and modifying the \texttt{main.py} file.
% say which function, what's its API, how can you test it - JJ
% this is not an API the need to write their own - Mario
% We can write an API later - M
% Anyway you need to say what is the signature of the function. Also, if they can use the existing implementation, you need to specify the license - JJ
If developers use an existing library for population-based algorithms, they need
to change the standard model of execution, that first creates a random
population because, in this case, the algorithm need to start with the population provided
as a parameter. Depending on the library, % Depending on which library? - JJ
it may be required to extract the population from the JSON message and replace
the population object created by the library. Again, the state of 
the population must be encoded as a JSON message to
be returned as a result. Additional data
must be returned in the JSON message, 
as depicted in  Listing \ref{code:result}. 
The output message contains the id of the worker container together
with records giving information about each iteration of the algorithm, 
including the best solution found. The controller uses this information 
to track the execution of the algorithm and keep a log in the Redis 
container for posterior analyses.

\begin{lstlisting}[language=JSON, caption=Fragment of output message, label=code:result ]
{
"time_stamp": 1588455316.698875,
"evals": [
  {
    "gen_num": 0, "best_fitness": -259.96925945939404,
    "best_solution": [ -4.9446848321611405, 
                        2.593007989886873, 
                        2.0011025031167673],
    "num_of_evals": 17
  },
  {
    "gen_num": 49, "best_fitness": -419.47555780783347,
    "best_solution": [ -0.9165294450108963, 
                        2.291966676472422, 
                        1.8527006568795485],
    "num_of_evals": 28
  }
],
"worker_id": "4f5eb12e-8278-40de-b0f3-4ac18171566d",
"message_counter": 1,
"message_id": "cbcd2e82-e232-4818-8aec-2cd072c7cfe9",
"best_score": -419.47555780783347
}
\end{lstlisting}

>>>>

In the case of the first level of integration, developers % a decoupler worker what? - JJ
% I think it was redundant, I was saying that in this level the worker container
% is not tied to the rest of the containers. - M 
can implement a new stateless Docker container following
the description in the previous section (\ref{workers}). The worker
container executes a daemon that continuously pulls messages from the input queue
on the Redis host specified as an environment variable {\texttt REDIS\_HOST}. If the new
population-based algorithm is written in Python, developers can base the new
implementation on the provided worker container image, adding a new algorithm
function and worker and modifying the \texttt{main.py} file. 
The worker must include a constructor with the configuration dictionary 
(see Listing \ref{code:config}) as the only parameter, and call a the new function 
with the required parameters, unpacking them from the configuration dictionary if necessary.
All the code of the EvoSwarm Application is published with the open source MIT license.
% say which function, what's its API, how can you test it - JJ
% this is not an API the need to write their own - Mario
% We can write an API later - M
% Anyway you need to say what is the signature of the function. 
%Also, if they can use the existing implementation, you need to specify the license - JJ

If developers use an existing library for population-based algorithms, they need
to change the standard model of execution, that creates first a random
population because, in this case, the algorithm needs to start with the
population provided as a parameter. Depending on the library used, % Depending on which library? - JJ 
it may be required to extract the population from the
JSON message and replace the population object created by the library. For
example, the DEAP library we used for the GA algorithm, creates the type of the
population at runtime (i.e., bit, float), so we have to replace the population
once DEAP created it. In the case of EvoloPy, the PSO method directly uses a
list of floats for storing the swarm, so we just added a parameter to receive
the population as a list of floats. Both libraries store information about each
iteration, so we just read it and put it in the format required.
Again, the state of the population must be encoded as a JSON message to be
returned as a result, with additional data as
depicted in Listing \ref{code:result}. The output message contains the id of the
worker container together with records giving information about each iteration
of the algorithm, including the best solution found. The controller uses this
information to track the execution of the algorithm and keep a log in the Redis
container for posterior analyses.

\begin{lstlisting}[language=Python, caption=Fragment of output message, label=code:result ]
{
"time_stamp": 1588455316.698875,
"evals": [
  {
    "gen_num": 0, "best_fitness": -259.96925945939404,
    "best_solution": [ -4.9446848321611405, 
                        2.593007989886873, 
                        2.0011025031167673],
    "num_of_evals": 17
  },
  {
    "gen_num": 49, "best_fitness": -419.47555780783347,
    "best_solution": [ -0.9165294450108963, 
                        2.291966676472422, 
                        1.8527006568795485],
    "num_of_evals": 28
  }
],
"worker_id": "4f5eb12e-8278-40de-b0f3-4ac18171566d",
"message_counter": 1,
"message_id": "cbcd2e82-e232-4818-8aec-2cd072c7cfe9",
"best_score": -419.47555780783347
}
\end{lstlisting}
